### 2015-07-02 narrative/proposed-work.tex
I probably messed up narrative/proposed-work.tex trying to merge in the changes to the broken version I had downloaded previously. My git-foo is not good enough to fix this properly so someone else needs to make sure this is correct. I am pretty sure it is wrong now.

Our research into the storage system and middle ware layers must address
many of these challenges including
% \begin{enumerate}
% \item How do we describe the user intentions at the API layer and have this
%   communicated down to the middle-ware and storage layers?
% \item How do we allow users to define their user defined compression
%   techniques and have this data read back from the storage system layers?
%   Where do we execute the decompression techniques 
% \item How do we evaluate the tradeoffs at runtime to guide data placement,
%   including the movement of data across the network, across the different
%   storage tiers? (data movement and quality tradeoff)
% \item Can we use different forms of learning techniques as daemons on the
%   system to perform data migration from one storage tier to another? For
%   example, if we see that a user is looking at one time slice after another
%   for a certain object in their dataset which is in the slower tiers of the
%   hierarchy, do we automatically propane up the data which has not been
%   requested in the hope that this will be requested data? (prediction and
%   prefetching, user defined compression on movement)
% \item Can we understand the true need of campaign storage and understand the
%   possible impact of the campaign storage if we run a hadoop-like
%   file-system instead of a lustre/gpfs file system? (additional layers)
% \item Can we limit the amount of data duplication? Data space is going to be
%   very constrained on the exascale system so we must ensure that minimal
%   copies are made of data, and when data is duplicated, they are removed
%   through a garbage collection routine. (space management)
% \item Can we build a model to give us the time estimates during the reading
%   and writing phases, so that rules can be in place from the user
%   perspective to make adaptive decisions. For example, if the file system
%   says that reading will take 3 months, users can they place in rules to
%   then read in a subset of data, and they can understand which data can be
%   read quickly and which pieces will take more time. (estimation)
% \item Can we understand how to place code in the system which will allow
%   data-regeneration to take place. (regeneration)
% \item How does the storage system do a better job in managing request from
%   all of the users on a LCF than today? We realize that today users who have
%   a better middlware system can often lock other users from getting high
%   performance when they are running. If we have the concept of currency
%   which is eventually used in the same extent as node-hours, then users will
%   have to be able to think about how much storage and how much bandwidth
%   they can choose. One question that needs to be understood is if there are
%   times when the system sees that there are very few storage system
%   resources being used, then the lucky users can get the bandwidth cheaper
%   than at times of heavy usage. How can we enforce this? (Fairness)
% \item How do we manage all of the metdata not only from the principle
%   objects, but from the sub-objects? How well will this scale when we have
%   users who can potentially create billions of objects from their
%   simulation? (scalability and discovery)

@@

\item Add plug-in architecture to Sirocco to support selective data compression
\item Add specific tier destinations command to Sirocco (assuming that the caching mechansism cannot achieve the desired effects).
\item Develop profiling system to determine how a data set is used during preparation runs prior to a capability run to determine how to optimize data placement for capability run analytics.

@@

% \input{narrative/data-desc}
\input{narrative/data-reduction} % includes data-reorg and the api specs move to the above section -
\input{narrative/data-reorg}
% \input{narrative/qos-app}
\input{narrative/placement}
% \input{narrative/policies}
% \input{narrative/apis}

@@

\input{narrative/migration}
\input{narrative/resource-mgmt}
\input{narrative/qos-storage}
% \input{narrative/discovery}
\input{narrative/eviction-metrics}
\input{narrative/naming-service}
% \input{narrative/time-estimation}
\input{narrative/infrastructure}

>>>>

{\bf {\color{red}Norbert will clean these pieces}}
Our research into the storage system and middle ware layers must address
many of these challenges including
% \begin{enumerate}
% \item How do we describe the user intentions at the API layer and have this
%   communicated down to the middle-ware and storage layers?
% \item How do we allow users to define their user defined compression
%   techniques and have this data read back from the storage system layers?
%   Where do we execute the decompression techniques 
% \item How do we evaluate the tradeoffs at runtime to guide data placement,
%   including the movement of data across the network, across the different
%   storage tiers? (data movement and quality tradeoff)
% \item Can we use different forms of learning techniques as daemons on the
%   system to perform data migration from one storage tier to another? For
%   example, if we see that a user is looking at one time slice after another
%   for a certain object in their dataset which is in the slower tiers of the
%   hierarchy, do we automatically propane up the data which has not been
%   requested in the hope that this will be requested data? (prediction and
%   prefetching, user defined compression on movement)
% \item Can we understand the true need of campaign storage and understand the
%   possible impact of the campaign storage if we run a hadoop-like
%   file-system instead of a lustre/gpfs file system? (additional layers)
% \item Can we limit the amount of data duplication? Data space is going to be
%   very constrained on the exascale system so we must ensure that minimal
%   copies are made of data, and when data is duplicated, they are removed
%   through a garbage collection routine. (space management)
% \item Can we build a model to give us the time estimates during the reading
%   and writing phases, so that rules can be in place from the user
%   perspective to make adaptive decisions. For example, if the file system
%   says that reading will take 3 months, users can they place in rules to
%   then read in a subset of data, and they can understand which data can be
%   read quickly and which pieces will take more time. (estimation)
% \item Can we understand how to place code in the system which will allow
%   data-regeneration to take place. (regeneration)
% \item How does the storage system do a better job in managing request from
%   all of the users on a LCF than today? We realize that today users who have
%   a better middlware system can often lock other users from getting high
%   performance when they are running. If we have the concept of currency
%   which is eventually used in the same extent as node-hours, then users will
%   have to be able to think about how much storage and how much bandwidth
%   they can choose. One question that needs to be understood is if there are
%   times when the system sees that there are very few storage system
%   resources being used, then the lucky users can get the bandwidth cheaper
%   than at times of heavy usage. How can we enforce this? (Fairness)
% \item How do we manage all of the metdata not only from the principle
%   objects, but from the sub-objects? How well will this scale when we have
%   users who can potentially create billions of objects from their
%   simulation? (scalability and discovery)

@@

\begin{enumerate}
\item Add plug-in architecture to Sirocco to support selective data compression
\item Add specific tier destinations command to Sirocco (assuming that the caching mechansism cannot achieve the desired effects).
\item Develop profiling system to determine how a data set is used during preparation runs prior to a capability run to determine how to optimize data placement for capability run analytics.

@@

%\input{narrative/data-desc}

{\bf {\color{red}Scott will integrate these pieces}}
\input{narrative/data-reduction} % includes data-reorg and the api specs move to the above section -
\input{narrative/data-reorg}

%\input{narrative/qos-app}
{\bf {\color{red}Hasan will integrate these pieces, Manish after Hasan}}
\input{narrative/placement}
\input{narrative/migration}
\input{narrative/eviction-metrics}

%\input{narrative/policies}
%\input{narrative/apis}

@@

{\bf {\color{red}Gary will integrate these pieces}}
\input{narrative/resource-mgmt}
\input{narrative/qos-storage}
%\input{narrative/discovery}
{\bf {\color{red}Jay  will integrate these pieces}}
\input{narrative/naming-service}
% \input{narrative/time-estimation}
\input{narrative/infrastructure}
